The Effects of Labor-Associated Drug Interventions on Neonatal Health Outcomes: A Predictive Analysis of Apgar5 Scores

### 2024-12-03 paper/paper.qmd
fix typos

In performing the analysis, we utilized several R packages. `tidyverse` [@tidyverse] was used for data manipulation, and `ggplot2`[@ggplot2] was used for visualizing results in graphical methods. `randomForest` [@randomForest] and `caret` [@caret] were used for Random Forest modeling while `rstanarm` [@rstanarm] was used for Bayesian linear modeling in the process of generating predictions.

@@

- Endpoint URL: `http://127.0.0.1:3505/predict_csv_local`

>>>>

In performing the analysis, we utilized several R packages. `tidyverse` [@tidyverse] was used for data manipulation, and `ggplot2` [@ggplot2] was used for visualizing results in graphical methods. `randomForest` [@randomForest] and `caret` [@caret] were used for Random Forest modeling while `rstanarm` [@rstanarm] was used for Bayesian linear modeling in the process of generating predictions.

@@

- Endpoint URL: [http://127.0.0.1:3505/predict_csv_local](http://127.0.0.1:3505/predict_csv_local)
